\bf Calendar-based graphics for visualizing people's daily schedules

### 2019-10-23 reviews/response.Rmd

We thank the reviewers for their helpful feedback which has improved the paper. The point by point description of changes are below: the reviewers' comments are in red and our response is in black.

# Associate editor {-}

> What if the data's collected over different time zones?

We added a short paragraph in Section 2.1 starting with "The R package, lubridate, ..." to address the time zone problem.

@@

We dropped figure 4 and 5 (diagrams for laying out the calendar).

> Figure 6. Could the figure have some indicator of the wrapping of few days to first row? It would help the reader.

We noted this in the figure caption. If adding some indicators, these indicators would possibly receive more attentions from the viewers, thus deemphasizing the main message.

> Somewhere in this section you should mention that labels and axes are discussed later.

Thanks. We have mentioned this at the end of Section 2.1.

@@

> "Would it be possible to have a plot for each day in a calendar plot with thick lines separating the months?  That kind of plot is common for calendar heatmaps."  I think that is important.  Perhaps they can build it in.  If not, why not?

The white space between months already emphasises the separations between months. The lines separating the months are also thicker than the ones separating the days in the calendar plot. These sit in the background to make the data plot more visible, which follows the Tufte's rules.

> The paper describes a display based on months.  Months have different lengths and are not comparable.  The paper says that a mixture of different plots is best.  A list of possible plots with pros and cons would be helpful.  Which features can be seen in one plot, which in another?

We recommend to make as many data plots as possible, including the calendar plots, to form a comprehensive picture about the data during the EDA process. Except for the calendar plots, the paper shows traditional displays in Figure 2, 3, and 11 as possible plots. The figure captions describe the main features that we can read from the plots. However, these typically focus on one temporal aspect, like time of day or day of week, which means that the information from other time resolutions cannot be seen. The calendar display is to complement them, laying out all possible resolutions simultaneously.

### 2019-10-23 calendar-vis.Rmd
done with response

The month labels located on the top left using $(\min{(x)}, \max{(y)})$ for every $(m, n)$. The weekday texts are uniformly positioned on the bottom of the whole canvas, that is $\min{(y)}$, with the central position of a cell $x / 2$ for each $j$.

@@

Figure \@ref(fig:calendar-elec) displays the global scaling of each household's data in a calendar layout, unfolding their day-to-day life via electricity usage. Glancing over household 1, their overall energy use is relatively low. Their weekday energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (January and February) for a couple of hours in the evening and weekends. In contrast, household 2 keeps a cooling system functioning for much longer hours, which becomes more evident from late Wednesday through Thursday to early Friday in mid-January. These observations help to explain the stripes and clusters of household 2 in Figure \@ref(fig:hod). It is difficult to give a succinct description of household 3 since everyday energy pattern is variable, but May and June see more structure than the previous months. Individual data can be idiosyncratic, hence aggregated plots like Figure \@ref(fig:dow) and \@ref(fig:hod) are essential for assembling pieces to form a picture. However, the calendar plots tell the stories that are untold by previous plots, for example, their vacation time. Household 1 is on vacation over three weeks of mid-June, and household 2 also took some days off in the second week of June. Further, household 3 takes one short trip in January and another one starting in the fourth week of June. Household 4 is away over two or three weeks in early April and late June. They all tend to take breaks during June probably due to the fact that the University winter break starts in June.

>>>>

The month labels located on the top left using $(\min{(x)}, \max{(y)})$ for every $(m, n)$. The weekday texts are uniformly positioned on the bottom of the whole canvas, that is $\min{(y)}$, with the central position of a cell $x / 2$ for each $j$. Formal axes and labels are discussed later in Section \@ref(sec:facet-calendar).

@@

Figure \@ref(fig:calendar-elec) displays the global scaling of each household's data in a calendar layout, unfolding their day-to-day life via electricity usage. Glancing over household 1, their overall energy use is relatively low. Their weekday energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (January and February) for a couple of hours in the evening and weekends. In contrast, household 2 keeps a cooling system functioning for much longer hours, which becomes more evident from late Wednesday through Thursday to early Friday in mid-January. These observations help to explain the stripes and clusters of household 2 in Figure \@ref(fig:hod). It is difficult to give a succinct description of household 3 since everyday energy pattern is variable, but May and June see more structure than the previous months. Individual data can be idiosyncratic, hence aggregated plots like Figure \@ref(fig:hod) are essential for assembling pieces to form a picture. However, the calendar plots tell the stories that are untold by previous plots, for example, their vacation time. Household 1 is on vacation over three weeks of mid-June, and household 2 also took some days off in the second week of June. Further, household 3 takes one short trip in January and another one starting in the fourth week of June. Household 4 is away over two or three weeks in early April and late June. They all tend to take breaks during June probably due to the fact that the University winter break starts in June.

### 2019-10-23 calendar-vis.tex
done with response

The month labels located on the top left using \((\min{(x)}, \max{(y)})\) for every \((m, n)\). The weekday texts are uniformly positioned on the bottom of the whole canvas, that is \(\min{(y)}\), with the central position of a cell \(x / 2\) for each \(j\).

@@

Figure \ref{fig:calendar-elec} displays the global scaling of each household's data in a calendar layout, unfolding their day-to-day life via electricity usage. Glancing over household 1, their overall energy use is relatively low. Their weekday energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (January and February) for a couple of hours in the evening and weekends. In contrast, household 2 keeps a cooling system functioning for much longer hours, which becomes more evident from late Wednesday through Thursday to early Friday in mid-January. These observations help to explain the stripes and clusters of household 2 in Figure \ref{fig:hod}. It is difficult to give a succinct description of household 3 since everyday energy pattern is variable, but May and June see more structure than the previous months. Individual data can be idiosyncratic, hence aggregated plots like Figure \ref{fig:dow} and \ref{fig:hod} are essential for assembling pieces to form a picture. However, the calendar plots tell the stories that are untold by previous plots, for example, their vacation time. Household 1 is on vacation over three weeks of mid-June, and household 2 also took some days off in the second week of June. Further, household 3 takes one short trip in January and another one starting in the fourth week of June. Household 4 is away over two or three weeks in early April and late June. They all tend to take breaks during June probably due to the fact that the University winter break starts in June.

>>>>

The month labels located on the top left using \((\min{(x)}, \max{(y)})\) for every \((m, n)\). The weekday texts are uniformly positioned on the bottom of the whole canvas, that is \(\min{(y)}\), with the central position of a cell \(x / 2\) for each \(j\). Formal axes and labels are discussed later in Section \ref{sec:facet-calendar}.

@@

Figure \ref{fig:calendar-elec} displays the global scaling of each household's data in a calendar layout, unfolding their day-to-day life via electricity usage. Glancing over household 1, their overall energy use is relatively low. Their weekday energy use is distinguishable from their weekends, indicating a working household. The air conditioner appears to be used in the summer months (January and February) for a couple of hours in the evening and weekends. In contrast, household 2 keeps a cooling system functioning for much longer hours, which becomes more evident from late Wednesday through Thursday to early Friday in mid-January. These observations help to explain the stripes and clusters of household 2 in Figure \ref{fig:hod}. It is difficult to give a succinct description of household 3 since everyday energy pattern is variable, but May and June see more structure than the previous months. Individual data can be idiosyncratic, hence aggregated plots like Figure \ref{fig:hod} are essential for assembling pieces to form a picture. However, the calendar plots tell the stories that are untold by previous plots, for example, their vacation time. Household 1 is on vacation over three weeks of mid-June, and household 2 also took some days off in the second week of June. Further, household 3 takes one short trip in January and another one starting in the fourth week of June. Household 4 is away over two or three weeks in early April and late June. They all tend to take breaks during June probably due to the fact that the University winter break starts in June.
